### 2018-05-04 msc_diploma_cubesat_galgoczi.tex
l

@@

ADC / energy calibration from measurement 20170829

illetve az egy chanellel: grb\_status3

>>>>

\subsection{1 channel setup}

\subsection{2 channel setup}

\includegraphics[width=100.0mm]{images/2channel.png}

\subsection{The satellite}

\includegraphics[width=100.0mm]{images/satellite.png}

\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
ANT		&  110		& Stainless Steel 	& 50\\
		&  & FR4 Glass-Epoxy sheet	& 50\\\hline
AUX		& 100	& 	FR4 Glass-Epoxy sheet	& 100\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline

Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline					
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline

 \hline
\end{tabular}
\end{center}

@@

%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3

1 channel read out:

\includegraphics[width=100.0mm]{images/irradiation.png}

\includegraphics[width=40.0mm]{images/positions.png}

The experimental results:

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.642 & 0.664 & & 70.7 & 0.743 & & 0.598 & &  \\ 
 \hline
\end{tabular}
\end{center}

The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of
40 cm:

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.3389 & 0.3256 & 0.3355 & 0.3521 & 0.3555 & 0.3522 & 0.2060 & 1 & 0.203  \\ 
 \hline
\end{tabular}
\end{center}

The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of 50 cm

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
 \hline
 Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
 Pos. of main peak & 0.4013 & 0.3917 & 0.3981 & 0.4045 & 0.4172 & 0.4140 & 0.2580 & 1 & 0.2739\\ 
 \hline
\end{tabular}
\end{center}

Reflectivity of 0.997 and abs. length of 60 cm

\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
 \hline
  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
  Pos. of main peak & 0.4588 & 0.4587 & 0.4697 & 0.4734 & 0.4700 & 0.4737 & 0.3388 & 1 & 0.3365  \\ 
 \hline
\end{tabular}
\end{center}
